---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# Rthingsboard

<!-- badges: start -->
<!-- badges: end -->

The goal of Rthingsboard is to provide interaction with the API of Thingsboard (https://thingsboard.io/), an open-source IoT platform for device management, data collection, processing and visualization. 



## Installation

You can install the released version of Rthingsboard from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("Rthingsboard")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("DDorch/Rthingsboard")
```
## Example

This is a basic example which shows you how to extract data from the following public dashboard : http://scada.g-eau.fr/dashboard/4db16100-f3e9-11e8-9dbf-cbc1e37c11e3?publicId=299cedc0-f3e9-11e8-9dbf-cbc1e37c11e3

### Load library

```{r setup}
library(Rthingsboard)
```

### Define the configuration parameters

```{r parameters}
# Identifier of SupAgro Halle hydraulique SCADA
url = "http://scada.g-eau.fr"
publicId = "299cedc0-f3e9-11e8-9dbf-cbc1e37c11e3"
entityId = "18d56d50-f3e9-11e8-9dbf-cbc1e37c11e3"
startDate = as.POSIXct("2020-11-19 9:30:00")
endDate = as.POSIXct("2020-11-19 17:00:00")

# Set logger threshold to DEBUG to see extra messages for debug purpose
logger::log_threshold(logger::DEBUG)
```

### Connexion to the Thingsboard server

First, you need to create an object of class `ThingsboardApi` as follow:

``` {r connection}
# Connection to the API
tb_api = ThingsboardApi(url = url, publicId = publicId)
```
### Retrieve data from the Thingsboard server

You can get the available keys on the specified device defined by its `entityId`:

``` {r getKeys}
# Get list of keys
keys = tb_api$getKeys(entityId = entityId)
```

Knowing the name of the available keys, you can get the telemetry of this device for a given period defined by `startTS` and `endTS`.

Here below, we download the telemetry for all keys beginning by "Y" and display the top of the table:

```{r getValues}
df <- tb_api$getValues(entityId,
                       keys = keys[grep("^Y", keys)],
                       startTs = startDate,
                       endTs = endDate)
knitr::kable(head(df))
```
You can then record this table into a file in the current directory:

```{r write_csv, eval=FALSE}
# getwd() # to get the path of the current directory
write.csv2(df, "myData.csv")
```

And also plot some time series:

```{r plot_telemetry}
library(ggplot2)
ggplot(df, aes(x = ts, y = value)) + 
  geom_line(aes(color = key), size = 1) +
  scale_color_brewer(palette = "Set1")
```

